According to the topics of the paper the relevant works can be divided into the next points:

\begin{itemize}
 \item  The Semantic Web area, coined by Tim Berners-Lee in 2001, has experienced during last years a growing commitment from both academia and industrial areas 
 with the objective of elevating the meaning of web information resources through a common and shared data model (graphs) and 
 an underlying semantics based on different logic formalisms (ontologies). The Resource Description Framework (RDF), based on a graph model, 
 and the Web Ontology Language (OWL), designed to formalize and model domain knowledge, are the two main \textit{ingredients} to reuse information and data 
 in a knowledge-based realm. Thus data, information and knowledge can be easily shared, exchanged and linked~\cite{Maali_Cyganiak_2011} 
 to other knowledge and databases through the use URIs, more specifically HTTP-URIs. Therefore the broad objective of this effort can be summarized 
 as a new environment of added-value services that can encourage and improve B2B (Business to Business), B2C (Business to Client) or 
 A2A (Administration to Administration) relationships by means of the implementation of new contex-awareness expert systems to tackle existing 
 cross-domain problems~\cite{DBLP:journals/cbm/GonzalezA13,DBLP:journals/eswa/Casado-LumbrerasGAP12} such as medical reasoning,
 analysis of social media, etc. in which data heterogeneities, lack of standard knowledge representation 
 and interoperability problems are common factors. As a practical view of the Semantic Web, 
 the Linked Data~\cite{Berners-Lee-2006,Heath_Bizer_2011} emerges to create a large and distributed database on the Web. 
 In order to reach this major objective the publication of information and data under a common data model (RDF) 
 and formats with a specific formal query language (SPARQL~\cite{Sparql11}) provide the required building blocks to turn the Web of documents 
 into a real database or ``Web of Data''. Research works are focused in two main areas: 1) production/publishing~\cite{bizer07how} and 2) consumption of 
 Linked Data. In the first case data quality~\cite{bizer2007,wiqa,ld-quality,DBLP:journals/ws/BizerC09,lodq,link-qa}, conformance~\cite{DBLP:journals/ws/HoganUHCPD12}, 
 provenance~\cite{w3c-prov,DBLP:conf/ipaw/HartigZ10}, trust~\cite{Carroll05namedgraphs}, description of datasets~\cite{void,Cyganiak08semanticsitemaps,ckanValidator} and 
 entity reconciliation~\cite{Serimi,Maali_Cyganiak_2011} are becoming major objectives since a mass of amount data is already available through 
 RDF repositories and SPARQL endpoints. 
 
 On the other hand, consumption of Linked Data is being addressed to provide new ways of data visualization~\cite{DBLP:journals/semweb/DadzieR11,hoga-etal-2011-swse-JWS}, 
 faceted browsing~\cite{Pietriga06fresnel, citeulike:8529753,Sparallax} and searching~\cite{hoga-etal-2011-swse-JWS}, processing~\cite{Harth:2011:SIP:1963192.1963318} and exploitation of data applying 
 different approaches such as sensors~\cite{Jeung:2010:EMM:1850003.1850235,ontology-search} and techniques such as distributed queries\cite{Hartig09executingsparql,Ankolekar07thetwo,sparqlOpt}, 
 scalable reasoning process~\cite{Urbani2010WebPIE,HoganHarthPolleres2009,DBLP:conf/semweb/HoganPPD10}, 
 annnotation of web pages~\cite{rdfa-primer} or information retrieval~\cite{Pound} to name a few.
  
 \item In the field of e-Procurement there are projects trying to exploit the 
 information of public procurement notices like the ``Linked Open Tenders Electronic Daily'' project~\cite{loted} 
 where they use the RSS feeds of TED.  In the European project LOD2~\cite{lod2-project}, there is a specific workpackage, 
 WP9a ``LOD2 for A Distributed Marketplace for Public Sector Contracts'', to explore and demonstrate the 
 application of linked data principles for procuring contracts in the public sector and, 
 the Media Lab research group at the Technical University of Athens has recently published the 
 ``PublicSpending.net''~\cite{publicspending} portal to visualize and manage statistics about public spending around the world. 
 Finally the ``OpenSpending.org''~\cite{open-spending} portal also presents some specifications to model public procurement data and 
 visualize where the money goes. In general, the ``LOD Around-the-Clock''~\cite{latc-project} (LATC) and PlanetData~\cite{planet-data-project} 
 projects are also increasing the awareness of LOD across Europe delivering specific research and dissemination activities such as the 
 ``European Data Forum''. Furthermore legal aspects of public sector information are being reviewed in the 
 LAPSI project~\cite{lapsi-project}. In the case of vocabularies and datasets, GoodRelations and ProductOntology are two o
 f the most prominent approaches for tagging products and services using semantic web technologies, 
 for instance Renault UK has GoodRelations in RDFa in their UK merchandise store.

\end{itemize}

 Since an overview of semantic technologies and Linked Data and their application to e-Procurement has been presented 
 some remarks and discussion about related works are outlined below.
 
 \begin{enumerate}
  \item  On the one hand, entity reconciliation is becoming a major challenge in the Linked Data community due to its relevance 
 to enrich data with existing datasets and to perform some kind of reasoning process. Existing techniques are based 
 on natural language processing (NLP) algorithms that perform some kind of string comparison (labels~\cite{Serimi} or URIs~\cite{Maali_Cyganiak_2011}) 
 to establish a similarity value between two RDF resources under a threshold of confidence. Tools such as the Silk~\cite{DBLP:conf/semweb/JentzschIB10} provides a 
 a tool for discovering relationships between data items within different Linked Data sources or the DBPedia Spotlight~\cite{DBLP:conf/i-semantics/MendesJGB11}, a 
 ``tool for automatically annotating mentions of DBpedia resources in text, providing a solution for linking unstructured information sources to the Linked Open Data 
 cloud through DBpedia'' are relevant tools for linking existing RDF resources. Other approaches coming from the ontology mapping and alignment areas try to create 
 links according to the structure (relationships) and naming convention of the RDF resources. Finally other approaches based on learning algorithms such as 
 genetic programming~\cite{DBLP:conf/semweb/IseleB11} are emerging to learn linkage rules from existing datasets. As conclusion interlinking RDF resources is 
 consider to be a key-enabler for a better data consumption. Neverthless the main drawback of these approaches lies in the necessity of human validation 
 to ensure the validaty and quality of the link. Furthermore these tools are based on two main assumptions: 1) resources are already available in RDF and 
 2) parameters such as stopwords cannot be easily configured. That is why it is necessary to provide a custom PSC reconciliation service that takes into account 
 the specific characteristics of PSCs descriptors after the promotion to RDF.
 
 \item On the other hand there is an increasing interest in the creation of methodologies, best practices/recipes~\cite{best-gld,linked-data-cookbook} and lifecycles~\cite{gld-lifecycle,lod2-stack}. In this sense, some 
 Linked Data design considerations can be found in~\cite{bizer07how} covering from the design or URIs~\cite{Sauermann+2007a,bernerslee1998uri,uris-uk}, design patterns~\cite{linked-data-patterns}, 
 publication of RDF datasets and vocabularies~\cite{Berr08}, etc. to the establishment of Linked Data profiles~\cite{basic-profile-w3c}. Neverthless all these guidelines present 
 a tangled environment of aspects with different levels of abstraction that prevent a clear application to a specific problem such as the promotion of PSCs to the Linked Data initiative.
 
%  \item Finally information retrieval and recommending processes have been widely studied to FIXME. In the case of Spreading Activation~\cite{Collins_Loftus_1975} (SA) it has been applied to the resolution
%   of problems trying to simulate the behavior of the brain using a connectionist method to provide an ``intelligent'' way to retrieve information and data. The use of SA was motivated 
%   due to the research on graph exploration~\cite{Scott1981,AndersonTheory}. Nevertheless the success of this technique is specially relevant to the fields of Document~\cite{turtle91inference} 
%   and Information Retrieval~\cite{Cohen1987}. It has been also demonstrated its application to extract correlations between query terms and documents analyzing user 
%   logs~\cite{Cui03} and to retrieve resources amongst multiple systems~\cite{Schumacher+2008search} 
%   in which ontologies are used to link and annotate resources. In recent years and regarding the emerging use of ontologies in the Semantic Web area new applications of SA have 
%   appeared to explore concepts~\cite{Qiu93,Chen95} addressing the two important issues: 1) the selection and 2) the weighting of 
%   additional search terms and to measure conceptual similarity~\cite{gouws-vanrooyen-engelbrecht:2010:CCSR}. 
%   On the other hand, there are works~\cite{DBLP:journals/cogsr/KatiforiVD10} exploring the application of the SA on ontologies in order to create context inference models. The 
%   semi-automatically extension and refinement of ontologies~\cite{liu_et_al_2005} is other trending topic to apply SA in combination with other techniques based on natural language processing. 
%   Data mining, more specifically mining socio-semantic networks\cite{paper:troussov:2008}, and applications to collaborative filtering (community detection based on tag recommendations, expertise location, etc.) 
%   are other potential scenarios to apply the SA theory due to the high performance and high scalability of the technique. In particular, 
%   annotation and tagging~\cite{labraTagging2007} services to gather meta-data~\cite{GelgiVD05} from the Web or to predict social annotation~\cite{Chen:2007:PSA:1780653.1780702} and recommending 
%   systems based on the combination of ontologies and SA~\cite{citeulike:3779904} are taken advantage of using SA technique. Besides 
%   semantic search~\cite{conf-sofsem-Suchal08} is a highlight area to apply SA following hybrid approaches~\cite{bopaEstonia,RochaSA04} or user query expansion~\cite{767402} combining metadata 
%   and user information.

 \end{enumerate}
  
